Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-07-06 WRITEUP/ms.tex
udpated Intro based on suggestion from DR via skype

\citestyle{aa}
\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131-1231 at $z$\,=\,0.65}
\shortauthors{Leung \& Riechers}

@@

\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131-1231 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the gravitationally lensed 
quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
RXS J1131-1231 ?. 
evidence for differential lensing.
wet-merger, Dynamical lens modeling
the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
% MBH-sigma relation...
\end{abstract}

@@

% - nearby: fixed proportion in M_BH to the M* in the bulge: ~0.1-0.2%
In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$\mstar ratio of high-$z$ galaxies falls below 
the local relation \citep[\eg][]{Walter04a, Borys05a, Riechers08a, Riechers08b}, implying 
high-$z$ AGNs grow faster than their host galaxies.
Yet, this relation is currently unconstrained at intermediate redshifts owing to the difficulties in measuring 
the stellar emission in the host galaxy under the presence of a quasar, or alternatively
the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is projected to different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for
their measurements in a relatively uncontaminated/independent manner.

In this paper, we study the molecular gas and dust properties of the quadruply imaged
quasar RXS J113151.62$-$123158 (hereafter RXJ1131) at
$z_\textrm{s, QSO}$\eq0.685 as lensed by an
elliptical galaxy at $z_\textrm{L}$\eq0.295. These redshifts 
are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
In the {\it HST} images presented by \citet[hereafter C06]{Claeskens06a}, emission 
in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius and
the quasar emission is lensed into four point-like images.
The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}
residing in RXJ1131 has been observed to 
be rotating with a high spin parameter
\citep[$a$\,$\sim$\,0.9;][]{Reis14a}.

This paper is structured as follows.
In \Sec{obs}, we outline the details of the observations and our data reduction process.
In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
and the resulting physical properties inferred for RXJ1131.
In \Sec{diss}, we discuss the merger stage of RXJ1131 and implications of 
this study in the context of the evolution of molecular gas content
and the $M_{\rm BH}$$-$\mdyn relation at intermediate redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Sluse03a}{S03}
\defcitealias{Claeskens06a}{C06}

@@

\subsection{ISM Properties} \label{sec:properties}
In this section, we derive the gas properties of the merging system
based on \bco and compare them with those reported by
C13 --- the largest sample of ULIRGs at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention,
we find a \fir luminosity of
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm70$)$\,\sfrU for RXJ1131.}.
Their results are based on unresolved \bco and \rot{4}{3} line observations with the
IRAM 30-m single-dish telescope.

@@

\subsubsection{Dynamical Mass}
Assuming the gas is virialized,
the dynamical mass can be approximate as
$M_{\rm dyn} = \sigma^2 R / G$,
where $\sigma$ is the velocity dispersion, or the rotational velocity in the case of a rotating disk model
$($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
we find a dynamical mass of
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
within the CO-emitting region in RXJ1131.
If we instead consider the
\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
We derive an inclination angle of 56.4$\degr$ from the
morphological axial ratio of $a/b\sim$1\farcs8$/$3\farcs25, which we estimate
from the source-plane image reconstructed by \citetalias{Claeskens06a} (Figure 3 in their paper).  
This corresponds to an inclination-corrected dynamical mass of
8.3\E{10}\Msun$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
Our estimate should be considered at best an upper limit since
the gas in RXJ1131 is unlikely virialized.
In the following sections, we use the
lower limit (8.3\pmm1.9)\E{10}\,\Msun as the dynamical mass as it is
derived in a manner similar to what is commonly used in literature 
(\eg \citetalias{Solomon97a}; \citealt[hereafter DS98]{Downes98a}; \citetalias{Greve05a}).
\defcitealias{Downes98a}{DS98}

Using the velocity dispersion obtained by fitting a single Gaussian to the
line profile of the companion ($\sigma$ = 30\,\kms)
and its intrinsic source size of $\sim$700\,pc obtained from the {\em HST}
$V$-band lens model \citepalias{Brewer08a},
we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 5\E{6}\,\Msun.
This corresponds to $M_{\rm dyn}$\,=\,2\E{7}\,\Msun if we assume an
inclination angle of 30$\degr$.
We adopt the $V$-band size as the radius $R$ in the above estimate 
owing to the fact that it is the least uncertain source size constraint available for the companion.
However, since this dynamical mass is substantially lower than the gas mass, which is 
a more reliable estimate based on the data in hand, 
we do not use this dynamical mass to derive other physical parameters.
The inconsistency between the gas mass of the companion and its dynamical mass
may indicate its dusty nature, which causes the $V$-band source size to 
appear much smaller than its true extent without any dust obscuration.
% On the other hand, we find a half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc from our lens 
% model, which can only serve as a crude measure of its unobscured source size (see \Sec{caveat}). Using this CO size, we find a dynamical mass of $M_{\rm dyn}$\,=\,3\E{7}\,\Msun. WHICH is STILL LOWER THAN the GAS MASS?

@@

\subsubsection{Gas Mass and Gas Ratios}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale gas-to-dust ratio of
40\pmm34, which is lower than the statistical average of $f_{\rm gas-dust}$\,=\,206
in the \citetalias{Combes13a} sample but well within their broad 
range of values over the entire sample. Our ratio is also consistent with 
high-$z$ SMGs 
% \citep[78\pmm26;][]{Bothwell13a} 
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
We note that the dust mass derived for RXJ1131 is poorly constrained.
If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
the dust mass is reduced by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\subsection{Fate of RXJ1131-1231}
The classical picture for mergers is one where they are responsible for the formation of the local
red and passive spheroidal galaxies.
With more realistic treatments of star formation and feedback in recent simulations,
it has been suggested that it is possible to suppress bulge formation
in gas-rich mergers, thereby forming large disks 
that resemble local spiral galaxies \citep{Springel05a, Robertson06a, Hopkins09a}.
% (bulge dominated; Springel05a, Robertson06a)
% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
%
%In systems that are sufficiently gas-rich, it is possible to
%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
%since there is little/no significant stellar material % (collisionless)
%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
%and gas will rapidly reform a cold disc in the background
%of the relaxing stellar potential.
%Gas, being collisional, cannot violently relax, but must
%have its angular momentum torqued away in order to dissipate and
%build a bulge by forming stars in a central starburst
%(\ie gas loses angular momentum to stars in the
%perturbed disk and fall toward center).
% In a merger,
%this torque is primarily internal, from stars in the same disc: the
%passages and merger of the secondary induce a non-axisymmetric
%distortion in the primary stellar and gas disc. The stellar distortion
%(in a trailing resonance and close proximity to the gas response)
%efficiently removes angular momentum from the gas and allows it
%to fall to the center and form a bulge  (see also Barnes \& Hernquist
% 1996).
% A bulge will form because cold gas with no angular momentum
% will be largely unable to form any sort of disk, and that a galaxy?s
% worth of gas compressed to high densities and small
% radii will inevitably form a large mass in stars).
%
% unlikely RXJ1131 will evolve into present-day massive
% ellipticals (M$\gtrsim$1\E{12}\,\Msun),
% gas-poor mergers: --> present-day massive elliticals
% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
The extended molecular gas distribution in RXJ1131 together with its low SFE implies that the 
removal of angular momentum of the gas via gravitational torque is inefficient.
Other mechanisms e.g. bar-like structures that are more efficient at removing angular momentum will 
be required in order to transform the gas disk of RXJ1131 into a stellar spheroid and evolve into 
an E/S0 galaxy. Without these, it is more conceivable that RXJ1131 will retain its disk component and
evolve into a disk galaxy upon its final coalescence with the companion.

@@

\subsection{The \bhrelation Relation}
Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
The dusty nature of this system?? \\

Efforts have been invested into calibrating and understanding how 
the use of or dynamical mass \citep[\eg]{Shields06a} 
as a proxy for stellar dispersion or bulge mass.

\citet{Shields06a} investigate the \bhrelation relation to high-$z$ using CO line width since 
CO has been detected in over hundreds of galaxies at $z$$>$1.
From their results, the dynamical mass from CO line widths is 
smaller than would be expected by the local relation, but they also noted it is possible that the stellar dispersion is
underestimated (see section 2.3 in Shields06a).

If we follow their approach, and use the CO linewidth to derive $\sigma_*$, assuming FWZI = 2$v_\textrm{rot}$, then the stellar dispersion is related to the CO dispersion via 
$\sigma_*$ = 4.44$\sigma_{\rm CO}$.
% FWHM ~ 2/3 FWZI; FWZI = 2*v_cir = 2sqrt(2) * sigma_*;  => FWHM ~ 0.53 sigma_*.
% where CO dispersion = FWHM/2.355 ---> sigma_* = 4.44 * CO dispersion.
, we find?.

If we adopt the broad H$\beta$ line as a proxy to the black hole mass using the virial method/estimator, then we find \mbh = 6\E{7}$-$1.3\E{8}\,\Msun \citep{Peng06a, Dai10a}, depending on the normalization.

%see Coppin08
%see section 5.2 in Bothwell13a
%
{\bf compare to J04135 in R13} \\

>>>>

\citestyle{aa}
\shorttitle{Molecular Gas in the Lensed Wet-Merger RXJ1131$-$1231 at $z$\,=\,0.65}
\shortauthors{Leung \& Riechers}

@@

\title{Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
RXJ1131 is gravitationally lensed quasar.
Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
RXS J1131-1231 a wet-merger, 
Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
% MBH-sigma relation...
\end{abstract}

@@

In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of high-$z$ submillimeter galaxies (SMGs) falls below 
the local relation \citep[\eg][]{Borys05a,Alexander08a} but that of high-$z$ quasar host galaxies are found 
lying above 
the relation \citep[\eg][]{McLure06a,Peng06a}.
Stellar mass of quasar host galaxies at $z$\,$>$\,4 constrained by their CO-based dynamical mass 
are also too small compared to that based from the local relation \citep{Walter04a, Riechers08a,Coppin08a}. 
It is evident that high-$z$ galaxies deviates from the local relation, and among their galaxy populations, but
the AGN-host galaxy connection at intermediate redshift is still poorly-constrained. 
This owes to the difficulties in measuring stellar emission in the host galaxy under the presence of a bright quasar, or alternatively
owing to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is projected to different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for the
relatively uncontaminated measurements of their emission.

\defcitealias{Sluse03a}{S03}
The ``Einstein ring'' RXS J113151.62$-$123158 (hereafter RXJ1131) 
at $z_\textrm{s, QSO}$\eq0.685 \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the 
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration and its redshift.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of radius 1\farcs83
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
We have thus carried out a detailed study for RXJ1131, as presented in this paper.
RXJ1131 is strongly lensed by an elliptical galaxy at $z_\textrm{L}$\eq0.295 \citepalias{Sluse03a}.
The black hole residing in RXJ1131 is rotating with a high spin parameter
\citep[$a$\,$\sim$\,0.9;][]{Reis14a}. 
Previous studies also report a black hole mass of
\mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}.

This paper is structured as follows.
In \Sec{obs}, we outline the details of the observations and our data reduction process.
In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
In \Sec{results}, we report measurements of the \bco and \cco lines and a compilation of photometric data from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
and the resulting physical properties inferred for RXJ1131.
In \Sec{diss}, we discuss the merger stage of RXJ1131, and the implications of 
this study in the context of the evolution of molecular gas content
and the $M_{\rm BH}$$-$\mdyn relation at intermediate redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

@@

\subsection{ISM Properties} \label{sec:properties}
In this section, we derive the gas properties of the merging system
based on \bco and compare them with those reported by
\citetalias{Combes13a} --- the largest sample of ULIRGs at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention,
we find a \fir luminosity of
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm70$)$\,\sfrU for RXJ1131.}.
Their results are based on unresolved \bco and \rot{4}{3} line observations with the
IRAM 30-m single-dish telescope.

@@

\subsubsection{Dynamical Mass}
Assuming the gas is virialized,
the dynamical mass can be approximate as
$M_{\rm dyn} = \sigma^2 R / G$,
where $\sigma$ is the velocity dispersion, or the rotational velocity in the case of a rotating disk model
$($\ie $\sigma$ = $V_{\rm rot}\, \sin\, i)$.
Using a rotational velocity $V_{\rm rot} \, \sin\, i$\,=\,345\,\kms (see \Sec{dynamics}),  % uncorrected for inclination
we find a dynamical mass of
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
within the CO-emitting region in RXJ1131.
If we instead consider the
\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun. %calc. using 2.32e5*6.22 * 200^2
We derive an inclination angle of 56.4$\degr$ from the
morphological axial ratio of $a/b\sim$1\farcs8$/$3\farcs25, which we estimate
from the source-plane image reconstructed by \citetalias{Claeskens06a} (Figure 3 in their paper).  
This corresponds to an inclination-corrected dynamical mass of
8.3\E{10}\Msun$<$\,$M_{\rm dyn}$\,$<$\,25\E{10}\Msun.
Our estimate should be considered at best an upper limit since
the gas in RXJ1131 is unlikely virialized.
In the following sections, we use the
lower limit (8.3\pmm1.9)\E{10}\,\Msun as the dynamical mass as it is
derived in a manner similar to what is commonly used in literature 
(\eg \citetalias{Solomon97a}; \citealt[hereafter DS98]{Downes98a}; \citetalias{Greve05a}).
\defcitealias{Downes98a}{DS98}

Using the velocity dispersion obtained by fitting a single Gaussian to the
line profile of the companion ($\sigma$ = 30\,\kms)
and its intrinsic source size of $\sim$700\,pc obtained from the {\em HST}
$V$-band lens model \citepalias{Brewer08a},
we find a dynamical mass of $M_{\rm dyn}$\,$\sin^2 i$ = 1.5\E{8}\,\Msun.
This corresponds to $M_{\rm dyn}$\,=\,5.8\E{8}\,\Msun if we assume an
inclination angle of 30$\degr$.
We adopt the $V$-band size as the radius $R$ in the above estimate 
owing to the fact that it is the least uncertain constraint on the source size for the companion.
However, since this dynamical mass is substantially lower than the gas mass, which is 
a more reliable estimate based on the data in hand, 
we do not use this dynamical mass to derive other physical parameters.
The underestimated dynamical mass may reflect
the dusty nature of the companion, which causes its $V$-band source size to 
appear much smaller than its true extent without any dust obscuration.
If we use the half-right radius of $R_{\rm CO}$\,=\,4.2\pmm2.8\,kpc obtained from our best-fit lens 
model as the unobscured source size (see \Sec{caveat}), we find a dynamical mass of 
$M_{\rm dyn}$\,=\,(3.5\pmm2.3)\E{9}\,\Msun (assuming $i$\eq30$\degr$), which is physically more sensible 
than that derived using the $V$-band source size. 
The uncertainty here only includes that of the CO source size.
Given the large systematic uncertainties associated with the model-based source size and
the lack of constraint on the inclination angle, we do not use this dynamical mass in the remaining of this paper.

@@

\subsubsection{Gas Mass and Gas Ratios}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale gas-to-dust ratio of
40\pmm34, which is lower than the statistical average of $f_{\rm gas-dust}$\,=\,206
in the \citetalias{Combes13a} sample but well within their broad 
range of values over the entire sample. Our ratio is also consistent with 
high-$z$ SMGs 
% \citep[78\pmm26;][]{Bothwell13a} 
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
We note that the dust mass derived for RXJ1131 is poorly constrained.
If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
the dust mass would reduce by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion} \label{sec:diss}
\subsection{Fate of RXS J1131$-$1231}
The classical picture for mergers is one where they are responsible for the formation of the local
red and passive spheroidal galaxies.
With more realistic treatments of star formation and feedback in recent simulations,
it has been suggested that it is possible to suppress bulge formation
in gas-rich mergers, thereby forming large disks 
that resemble local spiral galaxies \citep{Springel05a, Robertson06a, Hopkins09a}.
% (bulge dominated; Springel05a, Robertson06a)
% and disc with low B/D ratio ($\sim$0.1$-$0.2; Hopkins09a).
%
%In systems that are sufficiently gas-rich, it is possible to
%suppress the formation of a bulge in mergers of gas-rich discs (even in major merger)
%since there is little/no significant stellar material % (collisionless)
%available to torque away the cold gas in the disc, thus little/no angular momentum is lost,
%and gas will rapidly reform a cold disc in the background
%of the relaxing stellar potential.
%Gas, being collisional, cannot violently relax, but must
%have its angular momentum torqued away in order to dissipate and
%build a bulge by forming stars in a central starburst
%(\ie gas loses angular momentum to stars in the
%perturbed disk and fall toward center).
% In a merger,
%this torque is primarily internal, from stars in the same disc: the
%passages and merger of the secondary induce a non-axisymmetric
%distortion in the primary stellar and gas disc. The stellar distortion
%(in a trailing resonance and close proximity to the gas response)
%efficiently removes angular momentum from the gas and allows it
%to fall to the center and form a bulge  (see also Barnes \& Hernquist
% 1996).
% A bulge will form because cold gas with no angular momentum
% will be largely unable to form any sort of disk, and that a galaxy?s
% worth of gas compressed to high densities and small
% radii will inevitably form a large mass in stars).
%
% unlikely RXJ1131 will evolve into present-day massive
% ellipticals (M$\gtrsim$1\E{12}\,\Msun),
% gas-poor mergers: --> present-day massive elliticals
% (Boylan-Kolchin, Ma & Quataert 2005, 2006; Naab, Khochfar & Burkert 2006; Robertson B., Cox T. J., Hernquist L., Franx M., Hopkins P., Martini P., Springel V., 2006a, ApJ, 641, 21; Cox et al. 2006b)
The extended molecular gas distribution in RXJ1131 together with its low SFE implies that the 
removal of angular momentum of the gas via gravitational torque is inefficient.
Other mechanisms e.g. bar-like structures that are more efficient at removing angular momentum will 
be required in order to transform the gas disk of RXJ1131 into a stellar spheroid and evolve into 
an E/S0 galaxy. Without these, it is more conceivable that RXJ1131 will retain its disk component and
evolve into a disk galaxy upon its final coalescence with the companion.

@@

\subsection{The $M_{\rm BH}$$-$\mdyn Relation}
% the gas mass of RXJ1131 is 1.3\E{10}\,\Msun, 
% dynamical mass in RXJ1131 is $\sim$8.3\E{10}\,\Msun 
% total dust mass in the merging system is $\sim$2-4\E{8}\,\Msun,  % using CO magnification factor
Assuming RXJ1131 follows the local $M_{\rm BH}$$-$$M_{\rm bulge}$ relation reported by \citet{HR04a}, 
the virial-based black hole mass \mbh$\sim$\,6\E{7}\,\Msun \citep{Peng06a} corresponds 
to a stellar bulge mass of $M_{\rm bulge}$\eq4.2\E{10}\,\Msun.
This implies that the bulge component is responsible for making up roughly half the dynamical mass. 
If we subtract the black hole mass, gas mass, and dust mass\footnote{Here, we adopt the lowest dust mass among the two SED models to derive an upper limit on the stellar mass.}
from the dynamical mass and ignore a contribution from the dark matter, this would
yield an upper limit on the stellar mass of 6.8\E{10}\,\Msun. 
Thus, the bulge mass derived above based on the local relation is not physically infeasible.
The stellar mass upper limit would also imply a lower limit on the 
$M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $\sim$0.09\%, which falls below the local relation 
but is consistent within the range found in other intermediate-$z$ radio-loud AGNs \citep{McLure06a}. 
A dark matter fraction of over $f_{\rm DM}$\ssim0.6 would be needed for RXJ1131 to 
lie above the local relation and fall outside the range of $M_{\rm BH}$$/$$M_{\rm bulge}$ found in 
\citep{McLure06a}. 
% local: $M_{\rm BH}$/$M_{\rm bulge}$\ssim0.14\% or equivalently $\log{M_{\rm BH}/M_{\rm bulge}}$\ssim$-$2.85,

\subsection{Dynamical lens modeling of high-$z$ quasars}
%
Riechers08a is the only other similar system at emission in host galaxy lensed into an Einstein ring configuration and
with dynamical lens modeling of CO.
Which also velocity gradient.
Constraints on the.

\subsection{Others}
Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
The dusty nature of this system?? \\
compare to Riechers08a \\=
{\bf compare to J04135 in R13} \\
